Stack Safety as a Security Property

### 2020-07-08 main.tex
Fix definition 6.4
Remove vestigial notation and use the parts that are implicitly
defined by the new notation, with some trivial lifting of steps.

\definition
%
  Our testing property extends the basic tests above to whole variant
  stacks.  Given a machine that steps $(\mach, \pol) \hookrightarrow_P
  (\mach', \pol', \obs)$, say that a variant stack $\vs$ \iflater that
  is well-formed with respect to $\mach$\fi safisfies the
  \emph{variant stack test} if for each variant element $\vm{C}$
  (which is a variation of $\mach$ for $C$), $\vm{C}$ can take a step
  $\mathit{curr\_variant}(\vse) \stepstoobs{\obs} \mach'$ while
  satisfying the stack integrity test $\mathit{int}_T ~ \contour(\vse)
  ~ \mach ~ \mach'$ and stack confidentiality test $\mathit{conf}_T ~
  \mach ~ \mach'$ with regard to the original machine state. We write
  this $\mathit{\vs}_T ~ (\mach, \pol) ~ \vs$.

>>>>

\definition
%
  Our testing property extends the basic tests above to whole variant
  stacks.  Given a machine that steps $(\mach, \pol) \hookrightarrow_P
  (\mach', \pol', \obs)$, say that a variant stack $\vs$ \iflater that
  is well-formed with respect to $\mach$\fi safisfies the
  \emph{variant stack test} if for each variant element $\vm{C}$
  (which is a variation of $\mach$ for $C$), $\vm{C}$ can take a step,
  denoted $\vm{C} \stepstoobs{\obs} \mach'$, while
  satisfying the stack integrity test $\mathit{int}_T ~ C
  ~ \mach ~ \mach'$ and stack confidentiality test $\mathit{conf}_T ~
  \mach ~ \mach'$ with regard to the original machine state. We write
  this $\mathit{\vs}_T ~ (\mach, \pol) ~ \vs$.
